Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
wording

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classified the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
spuriously leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating
those algorithms.

>>>>

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classified the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating
those algorithms.
